\section{Grading}

{\bf All deliverables must be submitted to Git} (master branch) by the
submission deadline announced on Moodle.

You are expected to work in a team of {\bf four students}.  If needed,
the course coordinator may permit the creation of a team of 5
students.  Each team is responsible for dividing up the work and
coordinating as needed.

\subsection{BTI 3021}
You can earn 14, 14 and 22 points in the three networking sprints, for
a total of 50 points.  A canonical team will need {\bf 37 points} to
pass the networking component of BTI 3021.

\subsection{BTI 3022}
You can earn 14 and 22 points in the three networking sprints, for
a total of 36 points.  A canonical team will need {\bf 27 points} to
pass the networking component of BTI 3022.

\subsection{BTI 302x repeaters}

You can earn 24 points in a single sprint.
A team of two will need all {\bf 24 points}
pass the networking component of BTI 302x
when repeating.
A team of one will need {\bf 20 points} to
pass the networking component of BTI 302x
when repeating.

\subsection{Smaller teams for non-repeaters}

If your team is {\bf for good reasons} smaller than four students, the
passing threshold will be lowered by {\bf 2 points} per ``missing''
student per sprint.  So a student going alone in BTI 3021 would still
need {\bf 19 points} to pass.

Teams may {\bf request} changes to team membership at the end of a
sprint, but must provide a {\bf justification} to the course
coordinator, who may approve or decline the request.
