\documentclass{article}
\usepackage{url}
\usepackage{upquote}

\title{BTI 3021: Networking Project - Sprint 2}

\author{Christian Grothoff}
\date{}

\begin{document}
\maketitle

\section{Introduction}

For this sprint you will write a precursor to an IP router.  This
precursor system is to realize the ARP protocol functionality of
an IP device.

While the driver and skeleton you are given is written in C, you may
use {\em any} language of your choice for the implementation (as long
as you extend the {\tt Makefile} with adequate build rules).  However,
if you choose a different language, be prepared to write additional
boilerplate yourselves.

How the ARP protocol works is expected to be understood from the
networking class. If not, you can find plenty of documentation and
specifications on the Internet.

The basic setup is the same as in the first sprint.

\subsection{Deliverables}

There will be two main deliverables for the sprint:

\begin{description}
\item[Implementation] You must {\bf implement the ARP protocol}. Your
  implementation must answer to ARP requests, and also itself
  have the ability to issue ARP requests and to cache ARP replies.
  For this, you are to extend the {\tt arp.c} template provided
  (or write the entire logic from scratch in another language).
\item[Testing] You must implement and submit your own {\bf test cases}
  by {\em pretending} to be the network driver (see below) and sending
  ARP requests or command-line inputs to your program and verifying that it
  outputs the correct frames. Additionally, you should perform
  {\em interoperability} tests against existing
  implementations (i.e. other notebooks from your team to ensure that
  your ARP protocol implementation integrates correctly with other
  implementations).
\end{description}

All deliverables must be submitted to Git (master branch)
by the submission deadline announced on Moodle.

\subsection{Functionality}

The goal is to implement a program {\tt arp} that:
\begin{enumerate}
\item Watches for ARP queries on the Ethernet link and responds with ARP responses
  if queries are seen for your own IP address(es)
\item Provides an ARP cache so that it does not have to repeatedly
  make ARP requests to the network for MAC addresses it already knows.
\item Allows the user to trigger ARP requests via the console
  by reading ``arp`` commands with IPv4 addresses from {\tt stdin} (in human-readable format).
  The interactive command syntax should be
  ``arp {\em IP-ADDR} {\em IFNAME}'' (i.e. each line is to be prefixed with
  the letters ``arp '', followed by the IPv4 address and the name of
  the network interface).
  \begin{enumerate}
  \item
  If the {\tt IP-ADDR} is in the ARP cache, the program must immediately
  output the associated {\em MAC}:
\begin{verbatim}
28:c6:3f:1a:0a:bf
\end{verbatim}
  \item
  If the {\tt IP-ADDR} is {\bf not} in the ARP cache, the program should {\em only}
  issue the ARP query for those IPv4 addresses.
  \end{enumerate}
\item If an ARP request for one of your IP addresses
  or an ARP response destined for your system (IP and MAC)
  is received (at any time), the ARP cache must be
  updated accordingly. However, the MAC address MUST NOT be output at
  that time, even if there was an explicit command-line request for this
  address before.
\item If the user just enteres ``arp'' without
  an IP address, you should output the ARP table in the format
  ``{\em IP} -$>$ {\em MAC} ({\em IFNAME})'' with one entry per line,
  i.e.
\begin{verbatim}
10.54.25.15 -> 28:c6:3f:1a:0a:bf (eth1)
\end{verbatim}
  (note the leading ``0'' digit in {\tt 0a}).
\end{enumerate}

Your programm should be invoked with the name of the interface, the IP
address\footnote{You may support multiple IPs per network interface,
  using a comma-separated list of IPs and network masks, but this is
  not required.} for that interface and the network mask.  Example:
\begin{verbatim}
$ network-driver eth0 eth1 - \
  arp eth0[IPV4:192.168.0.1/16] eth1[IPV4:10.0.0.3/24]
\end{verbatim}
This means {\tt eth0} is to be bound to 192.168.0.1 (netmask 255.255.0.0)
and {\tt eth1} uses 10.0.0.3 (netmask 255.255.255.0).

The file {\tt arp.c} provides a starting point where the parsing of
the command-line arguments and the {\tt stdin}-interaction have been
stubbed for you.


\input{testing.tex}

\section{Grading}

\input{grading.tex}

\subsection{ARP grading}

You get points for each of the key deliverables:
\begin{center}
\begin{tabular}{l|r}
Correct implementation                    & 10 \\ \hline
Comprehensive test cases                  &  4 \\ \hline \hline
Total                                     & 14
\end{tabular}
\end{center}


\subsubsection{Correct implementation}
\begin{itemize}
  \item 10 points for passing test cases
\end{itemize}

\subsubsection{Comprehensive test cases}
\begin{itemize}
\item 0 points if public reference implementation (see Section~\ref{sec:binaries})
      fails test cases, {\bf otherwise}
\item 4 points for failing buggy implementations (see Section~\ref{sec:binaries})
\end{itemize}

\input{bonus.tex}

\input{setup.tex}

\section{Provided code}

\input{code.tex}

The main file for the exercise is {\tt arp.c}. In this file, you
should implement a program {\tt arp} which answers to ARP requests,
can initiate ARP requests from the command line and cache the answers.


\section{Provided binaries} \label{sec:binaries}

You are provided with several binaries:
\begin{description}
\item[reference-test-arp] A public test case, run using ``./reference-test-arp ./arp''
  to test your ARP implementation. Returns 0 on success.
\item[reference-arp] Reference implementation of the ``arp''.
\item[bug1-arp] Buggy implementation of a ``arp``.
\item[bug2-arp] Buggy implementation of a ``arp``.
\end{description}

\newpage
\section{Required make targets}

You may modify the build system. However, the final build system must
have the following {\tt make} targets:

\begin{description}
\item[all] build all binaries
\item[clean] remove all compiled files
\item[arp] build your ``arp`` binary from source; the binary MUST end up in the top-level directory of your build tree.
\item[test-arp] build your ``test-arp`` program from source; the program MUST end up in the top-level directory of your build tree.
\item[check-arp] Run ``test-arp`` against the ``arp'' binary.
\end{description}

For grading, we will basically run commands like:
\begin{verbatim}
GRADE=0
make test-arp
cp bug1-arp arp
make check-arp || GRADE=`expr $GRADE + 2`
cp bug2-arp arp
make check-arp || GRADE=`expr $GRADE + 2`
cp reference-arp arp
make check-arp || GRADE=0
echo "Test grade: $GRADE"
\end{verbatim}

You must thus make sure the build system continues to create programs in the
right (top-level) location!


\end{document}
