\documentclass{article}
\usepackage{url}
\usepackage{upquote}

\title{BTI 3021: Networking Project - Sprint 1}

\author{Christian Grothoff}
\date{}

\begin{document}
\maketitle

\section{Introduction}

For this sprint you will implement, document and test an Ethernet
switch in userland under GNU/Linux.

While the driver and skeleton you are given is written in C, you may
use {\em any} language of your choice for the implementation (as long
as you extend the {\tt Makefile} with adequate build rules).  However,
if you choose a different language, be prepared to write additional
boilerplate yourselves.

How an Ethernet switch works is expected to be understood from the
networking class. If not, you can find plenty of documentation and
specifications on the Internet.


\subsection{Deliverables}

There will be two main deliverables for the sprint:

\begin{description}
\item[Implementation] You must {\bf implement the switching
  algorithm}, extending the {\tt switch.c} template provided
  (or write the entire logic from scratch in another language).
\item[Testing] You must implement and submit your own {\bf test cases}
  by {\em pretending} to be the network driver (see below) and sending
  various Ethernet frames to your program and verifying that it
  outputs the correct frames. Additionally, you should perform
  {\em interoperability} tests against existing
  implementations (i.e. other notebooks from your team to ensure that
  your switch integrates correctly with other implementations).
\end{description}


\subsection{Functionality}

We will specifically also look for the following properties of a switch:
\begin{itemize}
\item Support for multicast and broadcast
\item Changing external connections (re-learning when devices move around the network)
\item Managing an ``attacker'' process that sends from billions of MAC
  addresses.  Ensure your switch's learning table uses finite memory.
\end{itemize}

\input{testing.tex}

\input{grading.tex}

\subsection{Switch grading}

For the {\bf switch} sprint, you get points for each of the key deliverables:
\begin{center}
\begin{tabular}{l|r}
Correct implementation                    &  8 \\ \hline
Comprehensive test cases                  &  6 \\ \hline \hline
Total                                     & 14
\end{tabular}
\end{center}

\subsubsection{Correct implementation}
\begin{itemize}
  \item 8 points for passing test cases
\end{itemize}

\subsubsection{Comprehensive test cases}
\begin{itemize}
\item 0 points if public reference implementation (see Section~\ref{sec:binaries})
      fails test cases, {\bf otherwise}
\item 6 points for failing buggy implementations (see Section~\ref{sec:binaries})
\end{itemize}

\input{bonus.tex}

\input{setup.tex}

\section{Provided code}

\input{code.tex}

The main file for the exercise is {\tt switch.c}. In this file, you should
implement a program {\tt switch} which forwards frames received on any
interface to any other interface, but passively learns MAC addresses
and optimizes subsequent traffic.


\section{Provided binaries} \label{sec:binaries}

You are provided with several binaries:

\begin{description}
\item[reference-test-switch] A public test case, run using ``./reference-test-switch ./switch''
  to test your switch. Returns 0 on success.
\item[reference-switch] Reference implementation of the ``switch''.
\item[bug1-switch] Buggy implementation of a ``switch''.
\item[bug2-switch] Buggy implementation of a ``switch''.
\item[bug3-switch] Buggy implementation of a ``switch''.
\end{description}

\newpage
\section{Required make targets}

You may modify the build system. However, the final build system must
have the following {\tt make} targets:

\begin{description}
\item[all] build all binaries
\item[clean] remove all compiled files
\item[switch] build your ``switch`` binary from source; the binary MUST end up in the top-level directory of your build tree.
\item[test-switch] build your ``test-switch`` program from source; the program MUST end up in the top-level directory of your build tree.
\item[check-switch] Run ``test-switch`` against the ``switch'' binary.
\end{description}

For grading, we will basically run commands like:
\begin{verbatim}
GRADE=0
make test-switch
cp bug1-switch switch
make check-switch || GRADE=`expr $GRADE + 2`
cp bug2-switch switch
make check-switch || GRADE=`expr $GRADE + 2`
cp bug3-switch switch
make check-switch || GRADE=`expr $GRADE + 2`
cp reference-switch switch
make check-switch || GRADE=0
echo "Test grade: $GRADE"
\end{verbatim}

You must thus make sure the build system continues to create programs
in the right (top-level) location!

\end{document}
