\documentclass{article}
\usepackage{url}
\usepackage{upquote}

\title{BTI 3021: Networking Project - Repeaters}

\author{Christian Grothoff}
\date{}

\begin{document}
\maketitle

\section{Introduction}

This project is ONLY for students repeating BTI 3021!  Unlike the
three sprints for first-time students, you must work in teams of {\bf
  at most two students} for this project.  To pass the networking part
of BTI 3021, you must achieve a total of {\bf 24} points in this
project (for a team of two).  The deadline is the same deadline as for
sprint 3.

For this project you will implement, document and test an Ethernet
{\bf vswitch} in userland under GNU/Linux.

While the driver and skeleton you are given is written in C, you may
use {\em any} language of your choice for the implementation (as long
as you extend the {\tt Makefile} with adequate build rules).  However,
if you choose a different language, be prepared to write additional
boilerplate yourselves.

How an Ethernet virtual switch (vswitch) works is expected to be
understood from the networking class. If not, you can find plenty of
documentation and specifications on the Internet.


\subsection{Deliverables}

There will be two main deliverables for the sprint:

\begin{description}
\item[Implementation] You must {\bf implement the switching
  algorithm}, extending the {\tt vswitch.c} template provided
  (or write the entire logic from scratch in another language).
\item[Testing] You must implement and submit your own {\bf test cases}
  by {\em pretending} to be the network driver (see below) and sending
  various Ethernet frames (with and without VLAN tags)
  to your program and verifying that it
  outputs the correct frames. Additionally, you should perform
  {\em interoperability} tests against existing
  implementations (i.e. other notebooks from your team to ensure that
  your switch integrates correctly with other implementations).
\end{description}


\subsection{Functionality}

Implement {\em vswitch} which forwards frames received on any
interface to any other interface, passively learns MAC addresses,
and respects VLAN tags. As before, the command-line specifies the
list of network interfaces you should switch on, but with
additional options to specify the VLANS.  Example:
\begin{verbatim}
$ network-driver eth0 eth1 eth2 eth3 - \
  vswitch eth0[T:1,2] eth1[U:1] eth2[U:2] eth3[U:2]
\end{verbatim}
This is supposed to run VLANs 1 and 2 tagged on {\tt eth0},
and VLANs 1, 2 or 2 untagged on {\tt eth1}, {\tt eth2},
or {\tt eth3} respectively.  Network interfaces specified
without ``[]'' should operate untagged on VLAN 0.  It is
not allowed to have interfaces accept both tagged and
untagged frames.

You may want to test your implementation against the Netgear
switch of the lab. For example, you could
Bridge a tagged VLAN ({\tt VID}$=3$) from the Netgear switch ({\tt
  eth1}) with two untagged notebooks ({\tt eth2}, {\tt eth3}) using
your vswitch code.


We will specifically also look for the following properties of a vswitch:
\begin{itemize}
\item Adding and stripping VLAN tags
\item Proper separation of VLANs
\item Support for multicast and broadcast
\item Changing external connections (re-learning when devices move around the network)
\item Managing an ``attacker'' process that sends from billions of MAC
  addresses.  Ensure your vswitch's learning table uses finite memory.
  You may use a single global learning table or separate tables per VLAN.
\end{itemize}

\input{testing.tex}

\input{grading.tex}

\subsection{VSwitch grading}

For the {\bf vswitch} sprint, you get points for each of the key deliverables:
\begin{center}
\begin{tabular}{l|r}
Correct implementation                    & 18 \\ \hline
Comprehensive test cases                  &  6 \\ \hline \hline
Total                                     & 24
\end{tabular}
\end{center}

\subsubsection{Correct implementation}
\begin{itemize}
  \item 18 points for passing test cases
\end{itemize}

\subsubsection{Comprehensive test cases}
\begin{itemize}
\item 0 points if public reference implementation (see Section~\ref{sec:binaries})
      fails test cases, {\bf otherwise}
\item 6 points for failing buggy implementations (see Section~\ref{sec:binaries})
\end{itemize}

\input{bonus.tex}

\input{setup.tex}

\section{Provided code}

\input{code.tex}

The main file for the exercise is {\tt vswitch.c}. In this file, you should
implement a program {\tt vswitch} which forwards frames received on any
interface to any other interface, but passively learns MAC addresses
and optimizes subsequent traffic.


\section{Provided binaries} \label{sec:binaries}

You are provided with several binaries:

\begin{description}
\item[reference-test-vswitch] A public test case, run using ``./reference-test-vswitch ./vswitch''
  to test your vswitch. Returns 0 on success.
\item[reference-vswitch] Reference implementation of the ``vswitch''.
\item[bug1-vswitch] Buggy implementation of a ``vswitch''.
\item[bug2-vswitch] Buggy implementation of a ``vswitch''.
\item[bug3-vswitch] Buggy implementation of a ``vswitch''.
\end{description}


\section{Required make targets}

You may modify the build system. However, the final build system must
have the following {\tt make} targets:

\begin{description}
\item[all] build all binaries
\item[clean] remove all compiled files
\item[vswitch] build your ``vswitch`` binary from source; the binary MUST end up in the top-level directory of your build tree.
\item[test-vswitch] build your ``test-vswitch`` program from source; the program MUST end up in the top-level directory of your build tree.
\item[check-vswitch] Run ``test-vswitch`` against the ``vswitch'' binary.
\end{description}

For grading, we will basically run commands like:
\begin{verbatim}
GRADE=0
make test-vswitch
cp bug1-vswitch vswitch
make check-vswitch || GRADE=`expr $GRADE + 2`
cp bug2-vswitch vswitch
make check-vswitch || GRADE=`expr $GRADE + 2`
cp bug3-vswitch vswitch
make check-vswitch || GRADE=`expr $GRADE + 2`
cp reference-vswitch vswitch
make check-vswitch || GRADE=0
echo "Test grade: $GRADE"
\end{verbatim}

You must thus make sure the build system continues to create programs
in the right (top-level) location!

\end{document}
