\documentclass{article}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{positioning,calc,decorations.pathreplacing,shapes,fit}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{url}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{array, adjustbox,url}
\usepackage{pifont,marvosym} % wasysym
\usepackage{rotating,subfig}
\usepackage{xspace}

\title{BTI 3021: Networking Project - Kick off}

\author{Christian Grothoff}
\date{}

\begin{document}
\maketitle

\section{Introduction}

These exercises may help you get familiar with the provided environment.
They are {\bf not graded}.

\subsection{Implement a hub}

Implement {\tt hub} which forwards frames received on any interface to
all other interfaces ({\tt eth0} through {\tt eth3}), without changing
them at all.  The {\tt hub} binary should take the list of interfaces
to use on the command line.

\subsection{Frame parsing}

Extend the simple frame {\tt parser} to:
\begin{enumerate}
\item Output your system's MAC address(es) in the canonical human-readable format.
\item Output the source MAC, destination MAC, payload type and payload length
  of each frame received. Confirm your results with {\tt wireshark}.
\end{enumerate}

\input{setup.tex}

\section{Provided code}

\input{code.tex}

The main files for the exercise are: {\tt parser.c},
{\tt hub.c} and {\tt test-hub.c}.

\begin{description}
  \item[hub.c] Skeleton to implement a hub.
  \item[test-hub.c] A public test case, run using ``./test-hub ./hub'' to test your hub. Returns 0 on success.
  \item[parser.c] Skeleton to implement a protocol parser.
  \item[harness.h] API for harness.c
  \item[harness.c] Helper logic for writing automated test cases
\end{description}


\section{Provided make targets}

The provided build system has the following {\tt make} targets:

\begin{description}
\item[all] build all binaries
\item[clean] remove all compiled files
\item[hub] build your ``hub`` binary from source; the binary MUST end up in the top-level directory of your build tree.
\item[test-hub] build your ``test-hub`` program from source; the program MUST end up in the top-level directory of your build tree.
\item[check-hub] Run ``test-hub`` against the ``hub'' binary.
\end{description}


\end{document}
