\documentclass{article}
\usepackage{url}
\usepackage{upquote}

\title{BTI 3021: Networking Project - Sprint 3}

\author{Christian Grothoff}
\date{}

\begin{document}
\maketitle

\section{Introduction}

For this sprint you will write an IP router, building upon the
results from your previous sprint (ARP). You will most likely
want to copy large parts of your ARP code into the router logic.

While the driver and skeleton you are given is written in C, you may
again use {\em any} language of your choice for the implementation (as
long as you extend the {\tt Makefile} with adequate build rules).
However, if you choose a different language, be prepared to write
additional boilerplate yourselves.

How an IP router works is expected to be understood from the
networking class. If not, you can find plenty of documentation and
specifications on the Internet.

The basic setup is the same as in the first two sprints.

\subsection{Deliverables}

There will be two main deliverables for the sprint:

\begin{description}
\item[Implementation] You must implement an IPv4 router. Your
  implementation must answer to IP packets, and route them.
  For this, you are to extend the {\tt router.c} template provided
  (or write the entire logic from scratch in another language).
\item[Testing] You must implement and submit your own {\bf test cases}
  by {\em pretending} to be the network driver (see below) and sending
  IP packets or command-line inputs to your program and verifying that it
  outputs the correct frames. Additionally, you should perform
  {\em interoperability} tests against existing
  implementations (i.e. other notebooks from your team to ensure that
  your IP router implementation integrates correctly with other
  implementations).
\end{description}


\subsection{Functionality}

Implement {\tt router} which routes IPv4 packets:
\begin{enumerate}
\item Populate your routing table from the network interface configuration
  given on the command-line using the same syntax as with the {\tt arp}
  program.
\item Use the ARP logic to resolve the target MAC address.   Simply drop the IP
  packets for destinations where the next hop's MAC address has not yet been
  learned, and issue the ARP request to obtain the destination’s MAC instead
  (once per dropped IP packet).
\item Make sure to decrement the TTL field and recompute the CRC.
  % add link to logic implementing CRC?
\item Generate ICMP messages for ``no route to network'' (ICMP
    Type 3, Code 0) and ``TTL exceeded'' (ICMP Type 11, Code 0),
\item Support the syntax {\tt IFC[RO]=MTU} where {\tt MTU} is the
  MTU for IFC.  Example: {\tt eth0=1500}.  Implement and test IPv4 fragmentation
  (including {\em do not fragment}-flag support), including sending
  ICMP  (ICMP Type 3, Code 4).
\item Support dynamic updates to the routing table via {\tt stdin}.
  Base your commands on the {\tt ip route} tool.  For example,
  ``route list'' should output the routing table, and
  ``route add 1.2.0.0/16 via 192.168.0.1 dev eth0'' should add
  a route to {\tt 1.2.0.0/16} via the next hop {\tt 192.168.0.1}
  which should be reachable via {\tt eth0}.  Implement at least
  the {\tt route list}, {\tt route add} and {\tt route del} commands.
  The interface-specific (connected local network) routes that
  are added upon startup from the command-line must not need to be
  {\tt del}etable.
\end{enumerate}

The output of your routing table should have the following format:
\begin{verbatim}
192.168.0.0/255.255.0.0 -> 1.2.3.4 (eth0)
\end{verbatim}
Use 0.0.0.0 if there is no next hop (the target host is in the connected
LAN on the specified interface).  You may print the routing table
in any order. Do include locally connected networks.

Routing table entries for locally connected networks MUST NOT be
configured explictly (via ``route add``) but must be automatically
created when your router starts (from the command-line arguments). You
do not have to support removal of those routing table entries.


Note that your implementation must realize following functions of a
router:

\begin{itemize}
\item Basic IP handling (TTL, ICMP, Checksum) % IP TTL decremented, ICMP? Checksum?
\item Forwarding and routing % IP packets flow? Mac updated?
\item Address resultion and caching % ARP cache?
\item IP fragmentation % Use eth3 for testing
\end{itemize}


\input{testing.tex}

\section{Grading}

\input{grading.tex}

\subsection{Router grading}

You get points for each of the key deliverables:
\begin{center}
\begin{tabular}{l|r}
Correct implementation                    & 14 \\ \hline
Comprehensive test cases                  &  8 \\ \hline \hline
Total                                     & 22
\end{tabular}
\end{center}


\subsubsection{Correct implementation}
\begin{itemize}
\item 14 points for passing test cases
\end{itemize}

\subsubsection{Comprehensive test cases}
\begin{itemize}
\item 0 points if public reference implementation (see Section~\ref{sec:binaries})
      fails test cases, {\bf otherwise}
\item 8 points for failing buggy implementations (see Section~\ref{sec:binaries})
\end{itemize}

\input{bonus.tex}

\section{Provided code}

\input{code.tex}

The main file for the exercise is {\tt router.c}. In this file, you
should implement a program {\tt router} which implements an IPv4 router.


\section{Provided binaries} \label{sec:binaries}

You are provided with several binaries:

\begin{description}
\item[reference-test-router] A public test case, run using ``./reference-test-router ./router''
  to test your router. Returns 0 on success.
\item[reference-router] Reference implementation of the ``router''.
\item[bug1-router] Buggy implementation of a ``router``.
\item[bug2-router] Buggy implementation of a ``router``.
\item[bug3-router] Buggy implementation of a ``router``.
\item[bug4-router] Buggy implementation of a ``router``.
\end{description}

\newpage
\section{Required make targets}

You may modify the build system. However, the final build system must
have the following {\tt make} targets:

\begin{description}
\item[all] build all binaries
\item[clean] remove all compiled files
\item[router] build your ``router`` binary from source; the binary MUST end up in the top-level directory of your build tree.
\item[test-router] build your ``test-router`` program from source; the program MUST end up in the top-level directory of your build tree.
\item[check-router] Run ``test-router`` against the ``router'' binary.
\end{description}

For grading, we will basically run commands like:
\begin{verbatim}
GRADE=0
make test-router
cp bug1-router router
make check-router || GRADE=`expr $GRADE + 2`
cp bug2-router router
make check-router || GRADE=`expr $GRADE + 2`
cp bug3-router router
make check-router || GRADE=`expr $GRADE + 2`
cp bug4-router router
make check-router || GRADE=`expr $GRADE + 2`
cp refernece-router router
make check-router || GRADE=0
echo "Test grade: $GRADE"
\end{verbatim}
You must thus make sure the build system continues to create programs in the
right (top-level) location!


\end{document}
